Evolutionary rescue and reintroduction of resistant frogs allows recovery in the presence of a lethal fungal disease

### 2023-05-20 doc/manuscript/translocation.qmd
Delete comments and fix typo

<!--# render to pdf using `quarto render doc/manuscript/translocation.qmd --to pdf` -->

@@

<!--# Limit = 250 words. -->

@@

<!--# Limit = 120 words.   -->

@@

Results from our genomic analyses strongly suggest that natural selection for adaptive alleles and resulting increased resistance/tolerance is at least partially responsible for the reduced susceptibility of frogs in recovering populations.
We identified specific alleles and genomic regions showing signatures of selection between adjacent Bd-naive and recovering MYL frog populations, consistent with strong selection following Bd exposure.
Importantly, some regions under selection are associated with cellular and immunological mechanisms known to contribute to disease resistance, including in amphibians [@zamudio2020].
For example, the MHC plays an important role in immunity.
In our study, we identified a region that shows evidence of selection in recovering populations and contains eight genes associated with either the MHC Class I or Class III regions.
These results corroborate numerous previous studies linking MHC genes to amphibian resistance/tolerance against Bd [e.g., @savage2011; @bataille2015].
Similarly, the region with the strongest indication of directional selection (as measured by $\pi_{diff}$) contains the interferon-related gene GVINP1.
Several previous studies have found this gene to be differentially expressed during Bd infection [e.g., @grogan2018; @ellison2014] and in populations differing in Bd susceptibility [@grogan2018].
This gene is also strongly linked to disease in salmon, explaining a notable 20% of the resistance phenotype [@robledo2020; @robledo2018].
We also identified a region, characterized by high *F~ST~* and low $\pi_{diff}$, that contained the complement genes C6 and C7.
The complement system plays an important role in innate immunity [@rieraromo2016], and our results could indicate that balancing selection is acting in this region of the genome to favor a diverse set of alleles, as is known for C6 in humans [@soejima2005].
Finally, based on the analysis of individual outlier variants, the RIN3 gene showed a consistent pattern of allele frequency differences across all nine of the frog populations sampled in this study, indicating consistent selection in populations distributed across a wide geographic area.
This gene is associated with inflammation response and in *Xenopus* is highly expressed in wound stumps following amputation of tadpole tails [@fukazawa2009].
Also in this analysis, the outlier variant with the lowest p-value (uncharacterized gene LOC108802036) is located adjacent to a type I interferon gene (Np-IFNi2) in another frog genome [@gan2018], and together with GVINP1 further suggests the importance of interferon-related genes in this system.

@@

\

<!--# How to insert >= symbol in header and table cells? Move second sentence of caption to footnote.-->

>>>>

@@

@@

@@

Results from our genomic analyses strongly suggest that natural selection for adaptive alleles and resulting increased resistance/tolerance is at least partially responsible for the reduced susceptibility of frogs in recovering populations.
We identified specific alleles and genomic regions showing signatures of selection between adjacent naive and recovering MYL frog populations, consistent with strong selection following Bd exposure.
Importantly, some regions under selection are associated with cellular and immunological mechanisms known to contribute to disease resistance, including in amphibians [@zamudio2020].
For example, the MHC plays an important role in immunity.
In our study, we identified a region that shows evidence of selection in recovering populations and contains eight genes associated with either the MHC Class I or Class III regions.
These results corroborate numerous previous studies linking MHC genes to amphibian resistance/tolerance against Bd [e.g., @savage2011; @bataille2015].
Similarly, the region with the strongest indication of directional selection (as measured by $\pi_{diff}$) contains the interferon-related gene GVINP1.
Several previous studies have found this gene to be differentially expressed during Bd infection [e.g., @grogan2018; @ellison2014] and in populations differing in Bd susceptibility [@grogan2018].
This gene is also strongly linked to disease in salmon, explaining a notable 20% of the resistance phenotype [@robledo2020; @robledo2018].
We also identified a region, characterized by high *F~ST~* and low $\pi_{diff}$, that contained the complement genes C6 and C7.
The complement system plays an important role in innate immunity [@rieraromo2016], and our results could indicate that balancing selection is acting in this region of the genome to favor a diverse set of alleles, as is known for C6 in humans [@soejima2005].
Finally, based on the analysis of individual outlier variants, the RIN3 gene showed a consistent pattern of allele frequency differences across all nine of the frog populations sampled in this study, indicating consistent selection in populations distributed across a wide geographic area.
This gene is associated with inflammation response and in *Xenopus* is highly expressed in wound stumps following amputation of tadpole tails [@fukazawa2009].
Also in this analysis, the outlier variant with the lowest p-value (uncharacterized gene LOC108802036) is located adjacent to a type I interferon gene (Np-IFNi2) in another frog genome [@gan2018], and together with GVINP1 further suggests the importance of interferon-related genes in this system.

@@
